---
title: "HW10_answer"
author: "Guojing Wu"
date: "5/6/2019"
output:
    pdf_document:
    highlight: default
    number_sections: true
    citation_package:
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
fontsize: 10pt
geometry: margin=1in
bibliography:
biblio-style:
header-includes:
- \usepackage{indentfirst}
- \usepackage{graphicx}
- \usepackage{geometry}
- \usepackage{subfigure}
- \usepackage{amsmath}
- \usepackage{listings}
- \usepackage{tikz}
- \usetikzlibrary{matrix}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F, 
                      comment = "")
library(tidyverse)
library(survival)
library(KMsurv) # contains many interesting data sets
library(ggfortify) # more beautiful plot
library(survminer)
theme_set(theme_bw())
```

## Problem 1. Log-rank test

**Figure 1: KM curve for each group**

```{r}
dat.1 <- tibble(
  time = c(c(4, 12, 15, 21, 23), c(2, 6, 8, 10, 19)), 
  cens = c(c(1, 0, 1, 0, 1), c(1, 0, 0, 1, 1)),
  group = c(rep(1, 5), rep(2, 5))
)
res1 = survdiff(Surv(time, cens) ~ group, data = dat.1)
autoplot(survfit(Surv(time, cens) ~ group, data = dat.1))
```

We got the pvalue = `r round(1 - pchisq(res1$chisq, 1), 3)` $> 0.05$, so we fail to reject the null and state that there is not much a difference between group1 and group2.

## Problem 2. 

**Figure 2: KM curve for each strata**

```{r}
data("kidtran")
# autoplot(survfit(Surv(time, delta) ~ gender + race, data = kidtran))
ggsurvplot(survfit(Surv(time, delta) ~ gender + race, data = kidtran), conf.int=F)

res2.1 = survdiff(Surv(time, delta)~ gender + race, data = kidtran, subset = (gender == 1))
res2.2 = survdiff(Surv(time, delta)~ gender + race, data = kidtran, subset = (gender == 2))
```

* For male patient, the pvalue = `r round(1 - pchisq(res2.1$chisq, 1), 3)` $> 0.05$, so we fail to reject the null and state that there is not much a difference between black and white in male subgroup.

* For female patient, the pvalue = `r round(1 - pchisq(res2.2$chisq, 1), 3)` $< 0.05$, so we reject the null and state that there is differences between black and white in female subgroup.

## Problem 3

**Table 1: coefficients for each predictor**

```{r}
data("larynx")
larynx = larynx %>% 
  mutate(Z1 = ifelse(stage == 2, 1, 0), 
         Z2 = ifelse(stage == 3, 1, 0), 
         Z3 = ifelse(stage == 4, 1, 0), 
         Z4 = age)

res3 = coxph(Surv(time, delta) ~ Z1 + Z2 + Z3 + Z4 + Z1 * Z4, data = larynx, ties = 'breslow')
t(res3$coefficients) %>% knitr::kable()
```

* At a given time point and fixed age $k$, the hazard ratio for subjects in Stage II versus subjects in Stage I is $e^{-7.38 + 0.11 \times k}$.

* At a given time point, the log hazard ratio for subjects in Stage III versus subjects in Stage I is `r round(as.numeric(res3$coefficients[2]), 3)`, keeping age at diagnosis constant.

* At a given time point, the log hazard ratio for subjects in Stage IV versus subjects in Stage I is `r round(as.numeric(res3$coefficients[3]), 3)`, keeping age at diagnosis constant.

* At a given time point, for  patients who are in stage II, the hazard ratio is $e^{0.006+0.112}=1.12$ for 1 unit increase in age at diagnosis.

* At a given time point, for patients who are not in stage II, the log hazard ratio is `r round(as.numeric(res3$coefficients[4]), 3)`, for 1 unit increase in age at diagnosis. 

The relative risk of dying is $e^{-7.38+0.11 \times 50}$ = `r round(exp(res3$coefficients[1] + res3$coefficients[5] * 50), 3)` for a stage II patient of age 50 as compared to a stage I patient of the same age.


## Code

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```